Constructing a universe for the setoid model

### 2020-06-29 paper.tex
Further work: comparison with XTT.

>>>>

One question is how models of SeTT and XTT \todo{reference} are related (assuming both sides are restricted to comparable collections of type formers).
From a model of XTT, do we functorially obtain a model of SeTT?
What about the reverse direction, assuming we have type case in SeTT? \todo{insert reference to where we define/discuss this in this paper}
